Preprocess turk annotations (hand/face detection)

### 2019-12-16 annotations/face_hands/analysis/preprocess_turk_detections.Rmd

---
title: "Face/Hand Annotations "
output: html_notebook
---

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lmerTest)
library(viridis)
library(rhdf5)
library(magick)
library(egg)
theme_set(theme_few())
```

@@

@@

  for (trial_ind in trial_indexes){
    trial_data = data.frame(
      ## including HITId and HITTYpe
      this_response = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,"`"))),
      # this_response_label = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,".label`"))),
      full_image_path = eval(parse(text = paste0("jd$Input.img_src",trial_ind))),
      trial_number = trial_ind,
      HITID = jd$HITId,
      HITTypeId =jd$HITTypeId,
      WorkerID = jd$WorkerId
    )
    d.raw <- bind_rows(d.raw, trial_data)
  }
}

@@

```

### Sometimes we get NAs and they end up in ".label fields", but not every trial has them (so it throws errors in a loop). I'm too tired to write an appropriate function so just leaving those NAs for now but the data is there. Starter code is below.
```{r}

@@

### Write function to spit back category of sanity check images
```{r message=FALSE}
sanity_check_category = function(shorter_image_path){
 ## I hate this function but I couldn't make it work without 
## going down a regex rabbithole so here it is
  hands = str_detect(shorter_image_path,'hands')
  faces = str_detect(shorter_image_path,'faces')
  none = str_detect(shorter_image_path,'none')
  both = str_detect(shorter_image_path,'face-hands')

@@

bad_workers <- sanity_images_wrong %>%
  group_by(WorkerID) %>%
  summarize(wrong_sanity = n()) %>%
  filter(wrong_sanity > 6) # more than 50% wrong

>>>>

---
title: "Preprocess turk annotations (hand/face detection)"
output: html_notebook
---

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lmerTest)
library(viridis)
library(magick)
library(egg)
theme_set(theme_few())
```

@@

```{r}
f <- dir("turk_annotations_single/")
jf <- paste("turk_annotations_single/",f,sep="")
jd <- read_csv(jf)

summary <- jd %>%
  group_by(WorkerId) %>%
  summarize(count_images = n(), avg_time = mean(WorkTimeInSeconds))

jd$response = jd$`Answer.trial-1.label`

agreement <- jd %>%
  group_by(Input.img_src1) %>%
  summarize(agree = response[1] == response[2])
```

@@

  for (trial_ind in trial_indexes){
    trial_data = data.frame(
      ## including HITId and HITTYpe
      this_response = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,"`"))),
      full_image_path = eval(parse(text = paste0("jd$Input.img_src",trial_ind))),
      trial_number = trial_ind,
      HITID = jd$HITId,
      HITTypeId =jd$HITTypeId,
      WorkerID = jd$WorkerId
    )
    d.raw <- bind_rows(d.raw, trial_data)
  }
}

@@

## Would like to get rando responses in .label field here:

### Sometimes we get NAs and they end up in ".label fields", but not every trial has them (so it throws errors in a loop). I'm too tired to write an appropriate function so just leaving those NAs for now but the data is there. Starter code is below.

@@

### Write function to spit back category of sanity check images
```{r message=FALSE}
sanity_check_category = function(shorter_image_path){
 ## I hate this function but I couldn't make it work without 
## going down a regex rabbithole so here it is
  hands = str_detect(shorter_image_path,'hands')
  faces = str_detect(shorter_image_path,'face')
  none = str_detect(shorter_image_path,'none')
  both = str_detect(shorter_image_path,'face-hands')

@@

bad_workers <- sanity_images_wrong %>%
  group_by(WorkerID) %>%
  summarize(wrong_sanity = n()) %>%
  filter(wrong_sanity > 3) # more than 1/4 wrong
